\newpage

\TOCadd{Acknowledgements}

\begin{center}
ACKNOWLEDGEMENTS
\end{center}

%\section*{\Huge Acknowledgements}
%\noindent 

\noindent 
I would like to thank:

\begin{description}
\item[Dr. Robert Kowalewski]
	for giving me the opportunity to work on the ATLAS experiment and pursue my interests within it, vastly improving the quality of this work through your advice and expertise, and being the most supportive supervisor I could have asked for. 
\item[Dr. Randall Sobie]
	for the interesting and very rewarding work on ATLAS computing, and the support throughout. 
\item[Dr. Kenji Hamano]
         for the guidance and advice, which was invaluable to the mono-s analysis.
\item[Dr. Philipp Mogg]
	for graciously teaming up with me as analysis co-contact, and sharing your impressive expertise and insight throughout. 
\item[Dr. Rolf Seuster]
	for supporting my ATLAS computing work, and the many delightful conversations. 
\item[Dr. Richard Keeler]
	for your generosity in offering me an inspiring first exposure to physics research as an undergraduate student at a time when I wasn't really sure I was cut out for the field, and for your continued support and encouragement since then. 
\item[My parents and sisters]
	for encouraging me to carve my own path, and for your unwavering love and support at every twist and turn. 
\item[Struan Eamer]
	for being crazy enough to hike the Juan de Fuca trail in the middle of winter so I could meet you, and for changing my life ever since. 
\item[My friends]
	for reminding me that there's more to life than my computer. 
\end{description}
